The goal of this project is to obtain a performance profile for a Raspberry Pi model B computer. At this first milestone, we do some basic ground work by measuring general information that is necessary for accurately measuring all other aspects of the system, such as the time taken to perform a measurement, the time taken to invoke a procedure, the time taken to spawn a process, etc. These are activities which incur an inevitable overhead while taking measurements of any other system, so they must themselves be measured and accounted for. 

Our team consists of Joshua Marxen and David Lisuk. David wrote the code for experiments 1-3, and Joshua did so for experiments 4 and 5. We coded our profiling code in the C language. Our compiler is gcc version 4.8.3, as implemented in the Raspbian linux operating system. We disabled any compiler optimizations by compiling with the -O0 flag.

As of this writing, it is 5 AM in the morning, and I have been working since 8 PM the previous evening. The day before, David had set up a git repository and installed Raspbian on his Raspberry Pi, and I think he did some work before that too. This night, he worked from about 7PM to 12PM. We got a late start, simply because we were not aware that this project was due until two days before. So I've worked about 9 hours on this project (if 8-5 is not indeed 9 hours, please forgive my 5 AM math). As such, our results are incomplete, and their accuracy suffers from deficiencies. However, we have been able to identify these deficiencies, and come up with strategies to remedy them in future milestones of this project.